Brief Announcement: Tight Bounds for Online Balanced Re-Partitioning

### 2020-02-18 paper/podc20ba.tex
3.1 to appendix

\begin{proof}
  Observe that when the repartition is triggered by \TAlg, the resulting partitioning is component respecting.
  Otherwise, if it does not exist, \TAlg simply ends the phase and performs no repartition.

@@

\section{Todos}

\todo{Author anonymous conference! Done}

\todo{ACM format for review? Is there any specific format like this? With line numbers etc. Done}

\todo{CCS concepts are mandatory}

\todo{ACM Reference format starts with a "." Possibly we did not provide all info. Done}

>>>>

@@

\begin{proof}[Proof of Lemma~\ref{lem:1req}]
  Observe that when the repartition is triggered by \TAlg, the resulting partitioning is component respecting.
  Otherwise, if it does not exist, \TAlg simply ends the phase and performs no repartition.
